The Astropy Project

### 2017-12-10 main.tex
Several very small fixes
In particular:
- typos
- Unify style from "us" to "the astropy project"

The \astropypkg package has a regular release schedule consisting of new significant
releases every 6 months, with bugfix releases as needed \citep{ape2}.
The major releases contain new features or any significant changes, whereas
the bugfix releases only contain fixes to code or documentation but no new
features.
Some versions are additionally designated as ``Long-term support'' (LTS)
releases, which continue to receive bug fixes for 2 years following the release
with no changes to the API\@.
The LTS versions are ideal for pipelines and other applications, where API
stability is essential.
The latest LTS release (v2.0) is also the last one that supports \python 2; It
will receive bug fixes until the end of 2019 \citep{ape10}.

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing
astronomical files, and units) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation.\footnote{\url{http://docs.astropy.org/en/stable/}}
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.

@@

As of \astropypkg version 2.0, units and quantities, prevalent in most of its
subpackages, have become a key concept for using the package as a whole.
Units are intimately entwined in the definition of astronomical coordinates;
Thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
(see \sectionname~\ref{sec:coordinates}) depends on them.
For most other subpackages, quantities are at least accepted and often expected
by default.

@@

The \texttt{Table} object now allows \texttt{Quantity}, celestial
coordinate (\texttt{SkyCoord}), and date/time (\texttt{Time}) objects to
be used as columns. It also provides a general way for other user-defined
objects to be used as columns. This makes it possible, for instance, to easily
represent catalogs of sources or time series as in \astropy, while having both the
benefits of the \texttt{Table} object (e.g., accessing specific rows/columns
or groups of them and combining tables) and of, for example,
the \texttt{SkyCoord} or the \texttt{Time} classes (e.g., converting the
coordinates to a different frame or accessing the date/time in the desired time scale).

@@

FITS files are now loaded \emph{lazily} (this default behavior can be
deactivated, if needed), where all HDUs are not loaded until
requested. This should provide substantial speed-ups when using the
convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
get an HDU that is near the beginning of many in a file.

@@

Models are defined by their parameters and initialized by providing values for them. The
names of the parameters are stored in a list, \texttt{Model.param\_names}. Parameters are complex objects.
They store additional information -- default value, default unit, and parameter constraints. Parameter
values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
for which the the number of parameters and their names are defined by another argument.
A typical example is a polynomial model defined by its degree.
A model is evaluated by calling it as a function.

If an analytical inverse of a model exists it is already defined and can be
accessed  by calling \texttt{Model.inverse}. In addition, \texttt{Model.inverse} can be assigned
another model which represents a computed inverse.

@@

\package{astropy.modeling} provides several fitters which are wrappers around some of the \texttt{numpy} and \texttt{scipy.optimize} functions and provide support for specifying parameter constraints. The fitters take a model and data as input and return a copy of the model with the optimized parameter values set. The goal is to make it easy to extend the fitting framework to create new fitters. The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solution for linear models).

@@

Modeling also supports a plugin system for fitters, which allows using the
\astropypkg models with external fitters. An example of this is
\package{SABA}\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
Sherpa\footnote{\url{http://cxc.cfa.harvard.edu/contrib/sherpa/}}
and \package{astropy.modeling}, to bring the Sherpa fitters into \astropypkg.

@@

In this section, we describe these tools, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.

@@

The \astropy project is also spreading awareness of best practices in
community-driven software development.
This is important as most practicing astronomers were not explicitly taught
computer science and software development, despite the fact that a major
fraction of nearly every astronomer's workload today is related to software use
and development.
The \astropypkg package leads by example, showing all interested astronomers how
modern tools like \texttt{git} version control or continuous integration can
increase the quality, accessibility, and discoverability of astronomical
software without overly complicating the development cycle.
Within \astropy, all submitted code is reviewed by at least one, but typically
more, members of the \astropy community, who provide feedback to contributors
to help improve their skills.
As a community, we follow an explicit code of conduct \citep{ape8} and treat all
contributors and users with respect, provide a harassment-free environment, and
encourage and welcome new contributions from all.
Thus, while the \astropy project provides and develops software and tools
essential to modern astronomical research, it also helps to prepare the current
and next generation of researchers with the knowledge to adequately use,
develop, and contribute to those tools within a conscientious and welcoming
community.

>>>>

The \astropypkg package has a regular release schedule consisting of new significant
releases every 6 months, with bugfix releases as needed \citep{ape2}.
The major releases contain new features or any significant changes, whereas
the bugfix releases only contain fixes to code or documentation but no new
features.
Some versions are additionally designated as ``Long-term support'' (LTS)
releases, which continue to receive bug fixes for 2 years following the release
with no changes to the API\@.
The LTS versions are ideal for pipelines and other applications, where API
stability is essential.
The latest LTS release (v2.0) is also the last one that supports \python 2; it
will receive bug fixes until the end of 2019 \citep{ape10}.

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
% Adrian
The \astropy project aims to provide \python-based packages for all tasks that
are commonly needed in a large subset of the astronomical community.
At the foundation is the \astropypkg core package, which provides general
functionality (e.g., coordinate transformations, reading and writing
astronomical files, and units) or base classes for other
packages to utilize for a common interface (e.g., \texttt{NDData}).
In this section, we highlight new features introduced or substantially improved
since version v0.2 (previously described in \citealt{astropy}).  The \astropypkg
package 
provides a full log of changes\footnote{\url{https://github.com/astropy/astropy/blob/stable/CHANGES.rst}}
over the course of the entire project and more details about individual
subpackages are available in the documentation.\footnote{\url{http://docs.astropy.org/en/stable/}}
Beyond what is mentioned below, most subpackages have seen increased performance
since the release of the v0.2 package.

@@

As of \astropypkg version 2.0, units and quantities, prevalent in most of its
subpackages, have become a key concept for using the package as a whole.
Units are intimately entwined in the definition of astronomical coordinates;
thus, nearly all functionality in the \texttt{astropy.coordinates} subpackage
(see \sectionname~\ref{sec:coordinates}) depends on them.
For most other subpackages, quantities are at least accepted and often expected
by default.

@@

The \texttt{Table} object now allows \texttt{Quantity}, celestial
coordinate (\texttt{SkyCoord}), and date/time (\texttt{Time}) objects to
be used as columns. It also provides a general way for other user-defined
objects to be used as columns. This makes it possible, for instance, to easily
represent catalogs of sources or time series in \astropy, while having both the
benefits of the \texttt{Table} object (e.g., accessing specific rows/columns
or groups of them and combining tables) and of, for example,
the \texttt{SkyCoord} or the \texttt{Time} classes (e.g., converting the
coordinates to a different frame or accessing the date/time in the desired time scale).

@@

FITS files are now loaded \emph{lazily} (this default behavior can be
deactivated, if needed), where all HDUs are not loaded until
requested. This should provide substantial speed-ups when using the
convenience functions (e.g., \texttt{getheader()} or \texttt{getdata()}) to
get an HDU that is near the beginning in a file with many HDUs.

@@

Models are defined by their parameters and initialized by providing values for them. The
names of the parameters are stored in a list, \texttt{Model.param\_names}. Parameters are complex objects.
They store additional information -- default value, default unit, and parameter constraints. Parameter
values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
for which the number of parameters and their names are defined by another argument.
A typical example is a polynomial model defined by its degree.
A model is evaluated by calling it as a function.

If an analytical inverse of a model exists it can be
accessed  by calling \texttt{Model.inverse}. In addition, \texttt{Model.inverse} can be assigned
another model which represents a computed inverse.

@@

\package{astropy.modeling} provides several fitters which are wrappers around some of the \texttt{numpy} and \texttt{scipy.optimize} functions and provide support for specifying parameter constraints. The fitters take a model and data as input and return a copy of the model with the optimized parameter values set. The goal is to make it easy to extend the fitting framework to create new fitters. The optimizers available in \astropypkg version 2.0 are Levenberg--Marquardt, Simplex, SLSQP, and LinearLSQFitter (which is based on \texttt{numpy.linalg} that provides exact solutions for linear models).

@@

Modeling also supports a plugin system for fitters, which allows using the
\astropypkg models with external fitters. An example of this is
\package{SABA}\footnote{\url{https://github.com/astropy/saba}}, which is a bridge between
Sherpa \citep{sherpa},
and \package{astropy.modeling}, to bring the Sherpa fitters into \astropypkg.

@@

In this section, we describe these tools. %, including robust statistical estimators, circular statistics, periodograms, spatial statistics, and histogram binning.

@@

The \astropy project is also spreading awareness of best practices in
community-driven software development.
This is important as most practicing astronomers were not explicitly taught
computer science and software development, despite the fact that a major
fraction of nearly every astronomer's workload today is related to software use
and development.
The \astropypkg package leads by example, showing all interested astronomers how
modern tools like \texttt{git} version control or continuous integration can
increase the quality, accessibility, and discoverability of astronomical
software without overly complicating the development cycle.
Within \astropy, all submitted code is reviewed by at least one, but typically
more, members of the \astropy community, who provide feedback to contributors
to help improve their skills.
As a community, \astropy follows an explicit code of conduct \citep{ape8} and treats all
contributors and users with respect, provides a harassment-free environment, and
encourages and welcomes new contributions from all.
Thus, while the \astropy project provides and develops software and tools
essential to modern astronomical research, it also helps to prepare the current
and next generation of researchers with the knowledge to adequately use,
develop, and contribute to those tools within a conscientious and welcoming
community.
